### 2017-04-25 thesis/latex/thesis.tex
Thesis: stuff.

\documentclass[10pt]{article} % Font size - 10pt, 11pt or 12pt

@@

@@

Cells need to create asymmetric, heterogeneous structures inside themselves in order to function. However, as per the above quote, diffusive processes cannot create this asymmetry. How then do cells create heterogeneity? Motor proteins are part of the answer. Motor proteins are structures which use energy to create directed motion in cells. In broad terms, they are creators of asymmetry. This thesis will explore a hypothesis on how one such motor protein, Dynein, generates directed motion.\\

@@

\subsection{Interest builder}
Motor proteins are cellular structures which use chemical energy to do work and generate motion. Kinesin, myosin and dynein are the three main motor proteins in cells. Though these proteins have significantly different ancestors [cite], they all evolved into a single similar structure. In biology when a structure is evolved three separate times, it is a sign that nature has found an efficient way for solving a problem. How, then, do motor proteins work?\\

@@

Despite these differences, the two motors implement very similar chemical cycles to achieve motion. Both motors begin bound to the microtubule, then bind ATP, causing them to lift one foot off. They then hydrolyse the ATP, causing their feet to kick forward and rebind. They then

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{../../figures/kb-kub-contour}
  \caption{Heat map comparing $k_b$ and $k_{ub}$ values to time spent in the onebound state. Simulations run for XXXXX seconds at standard conditions shown in Table \ref{table:simulation-std-conditions}, with spring constants $c_b = c_m = c_t = 2.4\Delta G_{ATP}$, $L_s=22.1nm$ and $L_t=11.15nm$.}
  \label{fig:kb-kub-heatmap}
\end{figure}

@@

\section{Chapter: Results \& Discussion}
\subsection{Stepping behavior of fit model}
The ideal set of parameters found via the fitting process is shown in Table \ref{table:final-parameter-table}.\\

>>>>

\documentclass[defaultstyle,11pt]{article}
%% \documentclass[defaultstyle,11pt]{thesis}

@@

%% \title{Simulating a Brownian model of the dynein motor protein}
%% \author{E. L.}{Capek}

%% \otherdegrees{B.A., North Dakota State University, 2005 \\
%% 	      M.S., University of Reno, 2007}

%% \degree{Doctor of Philosophy}		%  #1 {long descr.}
%% 	{Ph.D., Rocket Science}		%  #2 {short descr.}

%% \dept{Department of}			%  #1 {designation}
%% 	{Rocket Science}		%  #2 {name}

%% \advisor{Prof.}				%  #1 {title}
%% 	{Ed Visor}			%  #2 {name}

%% \reader{Prof.~Rachel Goddard}		%  2nd person to sign thesis
%% \readerThree{Ms.~Thora Nea}		%  3rd person to sign thesis

%% \abstract{Yet to come.}

%% \dedication{Yet to come.}

%% \acknowledgements{Yet to come.}

@@

Cells need to create asymmetric, heterogeneous structures inside themselves in order to function. However, as per the above quote, diffusive processes cannot create this asymmetry. How then do cells create heterogeneous structures they need in order to exist? Motor proteins are part of the answer. Motor proteins are structures which use energy to create directed motion in cells. In broad terms, they are mechanical creators of asymmetry. This thesis will explore a hypothesis on how one such motor protein, Dynein, generates directed motion.\\

@@

\subsection{Motivation}
Motor proteins are cellular structures which use chemical energy to do work and generate motion. Kinesin, myosin and dynein are the three main motor proteins in cells. Though these proteins have significantly different ancestors \ref{cite}, they all evolved into a single similar structure. In biology when a structure is evolved three separate times, it is a sign that nature has found an efficient way for solving a problem. How, then, do motor proteins work?\\

@@

Despite these differences, the two motors implement very similar chemical cycles to achieve motion. Both feet begin bound to the microtubule, then one unbinds. This foot diffuses forward, then rebinds to the microtubule

@@

@@

\newpage
\section{Chapter: Results \& Discussion}
\subsection{Validating model}
The simulation was first validated for obeying the laws of physics, and in particular, the equipartition theorem. Figure \ref{fig:equipartition_agreement} shows how both models have their angular potential energy converge to the expected $\frac{n}{2}k_BT$ energy over time.\\

\subsection{Exploring the parameter space}
Once validated, the model was fit to experimental data. Figure \ref{fig:kb-kub-heatmap} shows a heat map of the behavior of simulations running at many different $k_b$ and $k_{ub}$ values. The color of each point represents the fit quality of a simulation's $\left<t_{ob}\right>$ value to experiment. As can be seen, a good fit is found in the $k_b=XX$, $k_{ub}=YY$ region.

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{../../figures/kb-kub-contour}
  \caption{Heat map comparing $k_b$ and $k_{ub}$ values to time spent in the onebound state. Simulations run for XXXXX seconds at standard conditions shown in Table \ref{table:simulation-std-conditions}, with spring constants $c_b = c_m = c_t = 2.4\Delta G_{ATP}$, $L_s=22.1nm$ and $L_t=11.15nm$. The fit quality of each simulation is decided by $\log_{10}\left(\frac{\left<t_{bb}\right>_{sim}}{\left<t_{bb}\right>_{exp}}\right)$, then fit to the colorbar on the right. Values over or under the colorbar bounds are rounded to the max (1.0 or -1.0).}
  \label{fig:kb-kub-heatmap}
\end{figure}

\subsection{Stepping behavior of fit model}
The ideal set of parameters found via the fitting process is shown in Table \ref{table:final-parameter-table}.\\
